---
title: "Squirrel activity: Data Preparation"
description: |
    The aim of the study is to investigate the influence of altered environmental urban parameters and direct human disturbance expressed by the lockdown together with animal predator risk parameters on the general activity of squirrels
author:
    - name: "Sinah Drenske"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-2247-6507
    - name: "Julie Louvrier"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-1252-1746
    - name: "Marius Grabow"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-0702-9642
    - name: "Conny Landgraf"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      #orcid_id: 0000-0000-0000-0000
    - name: "Stephanie Kramer-Schadt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-9269-4446
    - name: "Aimara Planillo"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0001-6763-9923
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      ## styling of code
        code_folding: true  ## if `true` you can expand and shrink code chunks
        toc: true            ## if `true` adds a table of content
        toc_depth: 2         ## level to be displayed in the table of content
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

* **Research question:** Which risk effects increase or decrease the overall activity of red squirrels in urban gardens?  
* **Study area:** Berlin 2019-2020 
* **Data:** Detection histories of squirrels, martens and cats from 4 seasons (spring 2019, autumn 2019, spring 2020, autumn 2020), already filtered as in Louvrier et al. 2021 + environmental information on camera stations.

# Setup

```{r packages, message=FALSE, warning=FALSE}
# install the package of our department
#remotes::install_github("EcoDynIZW/d6")

#this function loads and installs (if necessary) the specified packages from CRAN or GitHub. No previously installed packages are reinstalled or updated by default
d6::simple_load(c(#"camtrapR",
                  #"gdata", 
                  #"ggpubr", 
                  "here", 
                  "lubridate", 
                  #"plyr",
                  #"raster",
                  #"readxl", 
                  "skimr", 
                  "stringr", 
                  "tidyverse", 
                  "vroom"
))
```

# Data

```{r data}
##Camera Traps detection histories
#loading the environmental variables and using only the user IDs that are within the cov table
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- readRDS(here::here("data-raw", "r-raw", "stacked_raster_values_and_garden_CT_all_seasons_allcovs_Renamed2022_01_19.RDS"))

#already formatted and filtered data 
CT_act_date_formated <- readRDS(here::here("data-raw", "r-raw","CT_act_allspecies_NoDelta_filtered2022_01_19.RDS"))

## raw data of ALL variables of the gardens (we will extract some columns for additional explanatory variables)
all_garden_vars_pics_all_seasons <- vroom(here::here("data-raw", "r-raw", "mammals_de_b_camtrap_wtimpact_20210208.csv"))
```

## Format environmental data

Some columns exist twice - once in German and once in English. We delete the German ones Column 2 (project phase) has some mistakes, we delete it

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas[, -(2:7)]
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- droplevels(stacked_raster_values_and_garden_CT_all_seasons_no_nas)
```

### Change german names to english

```{r}
# garden type
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type[stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type == "Wohngrundstueck"] <- "garden"
stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type[stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type == "Kleingarten"] <- "allotment"
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
# compost type
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost)
stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost[stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost == "Offen"] <- "open"
stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost[stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost == "Geschlossen"] <- "closed"
stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost[stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost == "Keiner"] <- "none"
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost)
```

## Format environmental data including ALL variables

### Reduce the number of rows to one row per station

```{r}
unique_all_garden_vars <- unique(all_garden_vars_pics_all_seasons[, c(13:15, 26:30)])
```

### Define new variables

#### dogs_binary

If a pet is present at the station, regardless of whether the pet is always outside or only during the day, it is a 1, otherwise a 0.

```{r}
unique_all_garden_vars$dogs_binary <- 
  ifelse(test = unique_all_garden_vars$haustiere_Hund == "Nachts_Haus" | unique_all_garden_vars$haustiere_Hund == "Immer_Freigang", 
         yes = 1, 
         no = 0)
```

#### cats_binary

```{r}
unique_all_garden_vars$cats_binary <- 
  ifelse(test = unique_all_garden_vars$haustiere_Katze == "Nachts_Haus" | unique_all_garden_vars$haustiere_Katze == "Immer_Freigang", 
         yes = 1, 
         no = 0)
```

#### trees_of_interest

```{r}
unique_all_garden_vars$trees_of_interest <- 
  ifelse(test = unique_all_garden_vars$baeume_Buchen == "Ja" | unique_all_garden_vars$baeume_Eichen == "Ja" | 
                unique_all_garden_vars$baeume_Nadelbaueme == "Ja" | unique_all_garden_vars$baeume_Nussbaueme == "Ja" | 
                unique_all_garden_vars$baeume_Obstbaueme == "Ja", 
         yes = 1, 
         no = 0)
```

### combine this data set with the already filtered data sets

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas %>%
  left_join(y = unique_all_garden_vars[c(1,9:11)], by = c("Station" = "User_uid"))
```

### Change column types

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- 
  stacked_raster_values_and_garden_CT_all_seasons_no_nas %>%
  dplyr::mutate(across(.cols = c(garden_type, compost, dogs_binary, cats_binary, trees_of_interest),
                       .fns =  as.factor)) %>%
  droplevels()
```

## Format CT data

### Rename species

The species names are in german, we translate them to english

```{r}
unique(CT_act_date_formated$Species)
```

```{r}
CT_act_date_formated$Species[CT_act_date_formated$Species == "Biber"] <- "Beaver"
CT_act_date_formated$Species[CT_act_date_formated$Species == "cat"] <- "Cat"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Dachs"] <- "Badger"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Eichhörnchen"] <- "Squirrel"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Feldhasen"] <- "Hare"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Igel"] <- "Hedgehog"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Marder_(Baum-und_Steinmarder)"] <- "Marten"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Maus"] <- "Mouse"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Ratte"] <- "Rat"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Reh"] <- "Deer"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Rotfuchs"] <- "Red Fox"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Waschbär"] <- "Raccoon"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Wildkaninchen"] <- "Rabbit"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Wildschwein"] <- "Wild Boar"
```

### Reassign the project phases and seasons

Unfortunately there was a mistake in the seasons column (now called project_phase). We reassign them

```{r}
#let's create a list that would contain the dates of beginning and end for each season
list_date_monthly <- list()
list_date_monthly[[1]] <- c(as.Date("2018-10-07"),
                           as.Date("2018-11-04")) #P1
list_date_monthly[[2]] <- c(as.Date("2019-04-01"),
                           as.Date("2019-04-28")) #P2
list_date_monthly[[3]] <- c(as.Date("2019-09-30"), 
                           as.Date("2019-10-27")) #P3
list_date_monthly[[4]] <- c(as.Date("2020-03-30"),
                           as.Date("2020-04-26")) #P4
list_date_monthly[[5]] <- c(as.Date("2020-09-28"), 
                           as.Date("2020-10-26")) #P5
```

```{r}
# Reassign the number of the project phase and rename the column
CT_act_date_formated$project_phase <- 
  # nested ifelse statements to assign the correct project phase. if the date when the picture was taken, is between the first 2 dates of the list, it is project phase 1, if not the next ifelse follows and so on
  # Project phase 1
  ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[1]][1] & 
                CT_act_date_formated$Date <= list_date_monthly[[1]][2], 
         yes = 1, 
         # Project phase 2
         no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[2]][1] & 
                            CT_act_date_formated$Date <= list_date_monthly[[2]][2], 
                     yes = 2, 
                     # Project phase 3
                     no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[3]][1] & 
                                        CT_act_date_formated$Date <= list_date_monthly[[3]][2], 
                                 yes = 3, 
                                 # Project phase 4
                                 no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[4]][1] & 
                                                    CT_act_date_formated$Date <= list_date_monthly[[4]][2], 
                                             yes = 4, 
                                             # Project phase 5
                                             no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[5]][1] & 
                                                                CT_act_date_formated$Date <= list_date_monthly[[5]][2], 
                                                         yes = 5, 
                                                         no = 99)))))

# Compare the two columns. What changed?
table(CT_act_date_formated$Season)
table(CT_act_date_formated$project_phase)
table(CT_act_date_formated$Season == CT_act_date_formated$project_phase) # 44 pictures were the project phase was wrong
```

```{r}
CT_act_date_formated$Season <- ifelse(test = CT_act_date_formated$project_phase == 1 | 
                                             CT_act_date_formated$project_phase == 3 | 
                                             CT_act_date_formated$project_phase == 5, 
                                      yes = "autumn", 
                                      no = "spring")
table(CT_act_date_formated$Season)
```

### Add a column for Covid-19 lockdowns

In which seasons were there lockdowns? 4 and 5 (spring and autumn 2020)

```{r}
CT_act_date_formated$lockdown <- ifelse(test = CT_act_date_formated$project_phase == 4 | 
                                               CT_act_date_formated$project_phase == 5, 
                                        yes = 1, 
                                        no =  0)

table(CT_act_date_formated$lockdown)
```

### Separate weekdays and weekends

```{r}
# Set the locale to UTC, weeks start on Monday, show the day as number not with labels
CT_act_date_formated <- CT_act_date_formated %>% 
  mutate(date_wday = lubridate::wday(x = CT_act_date_formated$Date, 
                                     week_start = getOption("lubridate.week.start", 1), 
                                     locale = "UTC",
                                     label = FALSE, 
                                     abbr = FALSE)) %>% 
#binary variable for weekdays or weekends: 0 for weekends, 1 for weekdays
 dplyr::mutate(weekdays_binary = factor(ifelse(date_wday == "6" | date_wday == "7", "0", "1")))
```

### Remove rows with conflicted data

#### Wrong coordinates or outside Berlin
```{r}
table(CT_act_date_formated$Station %in% stacked_raster_values_and_garden_CT_all_seasons_no_nas$Station)
Ct_act_date_full <- CT_act_date_formated # save the full data set
```


```{r}
CT_act_data_wrong_station <- CT_act_date_formated %>%
  filter(!Station %in% stacked_raster_values_and_garden_CT_all_seasons_no_nas$Station)
# 199 pictures
```


```{r}
table(CT_act_data_wrong_station$Species)
unique(CT_act_data_wrong_station$Station) # 11 stations
```


```{r}
CT_act_date_formated <- CT_act_date_formated %>%
  filter(Station %in% stacked_raster_values_and_garden_CT_all_seasons_no_nas$Station) %>%
  droplevels()
# -199 rows
```


#### Data from the same station in different seasons

Is there data from a station in different seasons?

```{r}
CT_stations_phase <- CT_act_date_formated %>%
  group_by(Station) %>%
  summarise(count = n_distinct(project_phase))

CT_stations_phase[which(CT_stations_phase$count > 1), ]

# Station 1553 has data from different project phases. We do not know why, we will delete it
```

Are there strange values for the phases of different stations?

```{r}
options(max.print = 10000)
table(CT_act_date_formated$Station, CT_act_date_formated$project_phase)

# for stations 1769 and 1869 maybe wrong dates were specified. We delete them too
```

Remove the rows with conflicted information

```{r}
CT_act_data_wrong_station <- CT_act_date_formated
length(which(CT_act_date_formated$Station == 1553))
length(which(CT_act_date_formated$Station == 1769))
length(which(CT_act_date_formated$Station == 1869))
# we delete 100 rows

CT_act_date_formated <- CT_act_date_formated %>% 
  filter(Station != 1553 & Station != 1769 & Station != 1869)
```

Remove unnecessary stations from the table of the environmental variables

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas %>% 
  filter(Station != 1553 & Station != 1769 & Station != 1869)
```


### Change column types

```{r}
CT_act_date_formated <- 
  CT_act_date_formated %>%
  dplyr::mutate(across(.cols = c(Species, Season, weekdays_binary, project_phase, lockdown),
                       .fns =  as.factor)) %>%
  droplevels()
```

Add season, project phase and lockdown to the table of the environmental variables

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- CT_act_date_formated[, c(2,3,7,8)] %>%
  unique() %>%
  right_join(y = stacked_raster_values_and_garden_CT_all_seasons_no_nas, by = "Station")
```

### Filter by species of interest

We do not consider all species in our analysis. The species that are not considered are removed from the dataset

```{r}
CT_species_interest <- CT_act_date_formated %>%
  filter(Species == "Squirrel" | 
           Species == "Cat" | 
           Species == "Marten") %>%
  droplevels()
```

### Calculate time differences between pictures of the same species

When the motion sensors of the cameras were triggered, several photos were taken. We delete all photos that were taken within one minute of the previous photo. Then we recalculate the time difference between the remaining photos.

```{r}
CT_species_interest_time <- CT_species_interest %>%
  dplyr::group_by(Species, project_phase, Station) %>%
  dplyr::arrange(DateTimeOriginal) %>% 
  mutate(diff_samespecies = as.numeric(difftime(time1 = DateTimeOriginal, 
                                                time2 = dplyr::lag(DateTimeOriginal), 
                                                units = "mins"))) %>%
  ungroup() %>%
  mutate(diff_samespecies = case_when(
    is.na(diff_samespecies) ~ 999, 
    TRUE ~ diff_samespecies)) %>% 
  group_by(project_phase, Station, Date) %>%
  filter(diff_samespecies > 1) %>%
  ungroup() %>%
  dplyr::group_by(Species, project_phase, Station) %>%
  dplyr::arrange(DateTimeOriginal) %>% 
  mutate(diff_samespecies = as.numeric(difftime(time1 = DateTimeOriginal, 
                                                time2 = dplyr::lag(DateTimeOriginal), 
                                                units = "mins"))) %>%
  ungroup() %>%
  mutate(diff_samespecies = case_when(
    is.na(diff_samespecies) ~ 999, 
    TRUE ~ diff_samespecies)) %>% 
  group_by(project_phase, Station, Date) %>%
  filter(diff_samespecies > 1) %>%
  ungroup()
```

## Rearrange columns

In both the CT data and the environmental variables

```{r}
names(CT_species_interest_time)
```

```{r}
CT_species_interest_time <- CT_species_interest_time %>%
  dplyr::select(Species, Station, project_phase, Season, lockdown, 
                DateTimeOriginal, Date, Time, diff_samespecies, 
                date_wday, weekdays_binary) %>%
  dplyr::arrange(DateTimeOriginal) %>%
  droplevels()
names(CT_species_interest_time)
```

```{r}
names(stacked_raster_values_and_garden_CT_all_seasons_no_nas)
```

```{r}
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas %>% 
  dplyr::select(Station, project_phase, Season, lockdown, 
                garden_type, garden_size, Local_tree_cover, fence_height, 
                compost, dogs_binary, cats_binary, trees_of_interest, 
                Lat, Long, inside, pop_100, dist_water_100, imperv_100, 
                noise_100, tree_cover_100, distance_border, ) %>%
  dplyr::arrange(Station) %>%
  droplevels()
```

## Remove phase 1
There are 5 project phases, so in order to have the same number of phases per season, we will not include phase 1 in the analysis. So we have phase 2 and 4 in spring and phase 3 and 5 in autumn. Phase 2 and 3 were before the Corona pandemic, phase 4 and 5 took place during the pandemic, there was a lockdown in Germany (and many other countries). 

```{r}
# Remove pictures from phase 1
CT_species_interest_full <- CT_species_interest_time

CT_species_phase1 <- CT_species_interest_full %>%
  filter(project_phase == 1) %>%
  droplevels()

CT_species_interest_time <- CT_species_interest_time %>%
  filter(project_phase != 1) %>%
  droplevels()

# remove the cameras from the data per station
stacked_raster_values_and_garden_CT_all_seasons_no_nas_full <- stacked_raster_values_and_garden_CT_all_seasons_no_nas

stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas %>%
  filter(project_phase != 1) %>%
  droplevels()
```

### Description of phase 1 (test phase)
```{r}
CT_phase1 <- CT_species_phase1 %>% 
  dplyr::count(Species, project_phase, Date) %>% # 
  group_by(Species, project_phase) %>% 
  dplyr::summarize(n_overall = sum(n),
                   n_days = n(),
                   mean_day = mean(n), 
                   median_day = median(n), 
                   min_day = min(n), 
                   max_day = max(n))

CT_phase1

CT_per_species1 <- CT_species_phase1 %>% 
  #filter(project_phase == 1) %>%
  dplyr::count(Species, project_phase, Station) %>%
  group_by(Species, project_phase) %>% 
  dplyr::summarize(n_overall = sum(n), 
                   n_stations = n())

CT_per_species1
```


# Data overview

## Camera trap detection histories

Project phase 1: Fall 2018 Project phase 2: Spring 2019 Project phase 3: Fall 2019 Project phase 4: Spring 2020 Project phase 5: Fall 2020

```{r}
skim(CT_species_interest_time)
```

```{r}
skim(CT_species_interest)
```

```{r}
table(CT_species_interest$Species) 
table(CT_species_interest_time$Species)

# Difference
table(CT_species_interest$Species) - table(CT_species_interest_time$Species)
```

## Environmental variables

```{r}
skim(stacked_raster_values_and_garden_CT_all_seasons_no_nas)
```

```{r}
print("Garden types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
print("Compost types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost)
print("Compost types & garden types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost, stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
print("Dogs")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$dogs_binary)
print("Cats")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$cats_binary)
print("Trees of interest")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$trees_of_interest)
```

# Save data

```{r}
# # CT_act_date_formated
# saveRDS(object = CT_act_date_formated,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_act_date_proc_20230305.RDS"))
# 
# # CT Species interest
# saveRDS(object = CT_species_interest_time,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_species_interest_time_20230305.RDS"))
# 
# # CT Species interest full
# saveRDS(object = CT_species_interest_full,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_species_interest_time_full_20230305.RDS"))
# 
# # stacked_raster_values_and_garden_CT_all_seasons_no_nas
# saveRDS(object = stacked_raster_values_and_garden_CT_all_seasons_no_nas,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "stacked_raster_values_and_garden_CT_all_seasons_no_nas_proc_20230305.RDS"))
# 
# # stacked_raster_values_and_garden_CT_all_seasons_no_nas full
# saveRDS(object = stacked_raster_values_and_garden_CT_all_seasons_no_nas_full,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "stacked_raster_values_and_garden_CT_all_seasons_no_nas_proc_full_20230305.RDS"))
```

------------------------------------------------------------------------

<details>

<summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
