---
title: "Squirrel activity: Data Preparation" ## name of your project and analysis step
description: |
    The aim of this study is...
author:
    ## author information; single arguemnts can be deleted if not needed
    - name: "Sinah Drenske"
      url: https://izw-berlin.de/en/john-smith-en.html  
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0000-0000-0000
    - name: "Julie"
      url: https://janedoe.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0000-0000-0000
    - name: "Stephanie Kramer-Schadt"
      url: https://janedoe.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0000-0000-0000
    ## add more authors with the same intendation and styling if needed 
    ## a new author always starts with a hyphen!
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      ## styling of code
        code_folding: true  ## if `true` you can expand and shrink code chunks
        toc: true            ## if `true` adds a table of content
        toc_depth: 2         ## level to be displayed in the table of content
---

* **Research question:**
* **Study area:**
* **Data:** Already filtered data used by Julie .... in "...."


# Setup
## Packages
```{r packages, message=FALSE, warning=FALSE}
## for non-CRAN packages please keep install instruction
## but commented so it is not run each time, e.g.
# devtools::install_github("EcoDynIZW/template")

## libraries used in this script
## please add ALL LIBRARIES NEEDED HERE
## please remove libraries from the list that are not needed anymore 
## at a later stage
package.list=c("camtrapR",
               "dplyr",
               "evaluate",
               "ggplot2",
               "gdata",
               "here",
               "janitor",
               "lubridate",
               "maptools",
               # "optimbase", maybe needed but has to be installed from the CRAN archive https://cran.r-project.org/web/packages/optimbase/index.html
               "plyr",
               "raster",
               "readxl",
               #"rgdal",
               #"rgeos",
               #"rjags",
               "rlecuyer",
               #"sf",
               "showtext",
               "skimr",
               "snowfall",
               #"sp",
               "stringr",
               "tidyverse",
               "vroom"
               )

for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}

rm(package.list)
rm(package)
```

## Data
```{r data}
##Camera Traps detection histories
#loading the environmental variables and using only the user IDs that are within the cov table
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- readRDS(here::here("data-raw", "r-raw", "stacked_raster_values_and_garden_CT_all_seasons_allcovs_Renamed2022_01_19.RDS"))

#already formatted and filtered data 
CT_act_date_formated <- readRDS(here::here("data-raw", "r-raw","CT_act_allspecies_NoDelta_filtered2022_01_19.RDS"))
```

### Format environmental data
Some columns exist twice - once in German and once in English. We delete the German ones
```{r}
# column 3-7 will be removed
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- stacked_raster_values_and_garden_CT_all_seasons_no_nas[, -(3:7)]
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- droplevels(stacked_raster_values_and_garden_CT_all_seasons_no_nas)
```

### Format CT data
#### Rename species
the species names are in german, we translate them to english
```{r}
unique(CT_act_date_formated$Species)
```

```{r}
CT_act_date_formated$Species[CT_act_date_formated$Species == "Biber"] <- "Beaver"
CT_act_date_formated$Species[CT_act_date_formated$Species == "cat"] <- "Cat"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Dachs"] <- "Badger"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Eichhörnchen"] <- "Squirrel"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Feldhasen"] <- "Hare"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Igel"] <- "Hedgehog"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Marder_(Baum-und_Steinmarder)"] <- "Marten"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Maus"] <- "Mouse"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Ratte"] <- "Rat"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Reh"] <- "Deer"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Rotfuchs"] <- "Red Fox"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Waschbär"] <- "Raccoon"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Wildkaninchen"] <- "Rabbit"
CT_act_date_formated$Species[CT_act_date_formated$Species == "Wildschwein"] <- "Wild Boar"
```

#### Reassign the seasons
Unfortunately there was a mistake in the seasons column. We reassign the seasons
```{r}
#let's create a list that would contain the dates of beginning and end for each season
list_date_monthly <- list()
list_date_monthly[[1]] <- c(as.Date("2018-10-07"),
                           as.Date("2018-11-04")) #P1
list_date_monthly[[2]] <- c(as.Date("2019-04-01"),
                           as.Date("2019-04-28")) #P2
list_date_monthly[[3]] <- c(as.Date("2019-09-30"), 
                           as.Date("2019-10-27")) #P3
list_date_monthly[[4]] <- c(as.Date("2020-03-30"),
                           as.Date("2020-04-26")) #P4
list_date_monthly[[5]] <- c(as.Date("2020-09-28"), 
                           as.Date("2020-10-26")) #P5
```

```{r}
# Reassign the number of the project phase and rename the column
CT_act_date_formated$project_phase <- 
  # nested ifelse statements to assign the correct project phase. if the date when the picture was taken, is between the first 2 dates of the list, it is project phase 1, if not the next ifelse follows and so on
  # Project phase 1
  ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[1]][1] & 
                CT_act_date_formated$Date <= list_date_monthly[[1]][2], 
         yes = 1, 
         # Project phase 2
         no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[2]][1] & 
                            CT_act_date_formated$Date <= list_date_monthly[[2]][2], 
                     yes = 2, 
                     # Project phase 3
                     no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[3]][1] & 
                                        CT_act_date_formated$Date <= list_date_monthly[[3]][2], 
                                 yes = 3, 
                                 # Project phase 4
                                 no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[4]][1] & 
                                                    CT_act_date_formated$Date <= list_date_monthly[[4]][2], 
                                             yes = 4, 
                                             # Project phase 5
                                             no = ifelse(test = CT_act_date_formated$Date >= list_date_monthly[[5]][1] & 
                                                                CT_act_date_formated$Date <= list_date_monthly[[5]][2], 
                                                         yes = 5, 
                                                         no = 99)))))

# Compare the two columns. What changed?
table(CT_act_date_formated$Season)
table(CT_act_date_formated$project_phase)
table(CT_act_date_formated$Season == CT_act_date_formated$project_phase) # 44 pictures were the project phase was wrong
```

```{r}
CT_act_date_formated$Season <- ifelse(test = CT_act_date_formated$project_phase == 1 | 
                                             CT_act_date_formated$project_phase == 3 | 
                                             CT_act_date_formated$project_phase == 5, 
                                      yes = "autumn", 
                                      no = "spring")
table(CT_act_date_formated$Season)
```


# Data overview
## Camera trap detection histories
Project phase 1: Fall 2018 
Project phase 2: Spring 2019
Project phase 3: Fall 2019
Project phase 4: Spring 2020
Project phase 5: Fall 2020

```{r}
skim(CT_act_date_formated)
```


## Environmental variables
```{r}
skim(stacked_raster_values_and_garden_CT_all_seasons_no_nas)
```


```{r}
print("Cams per Season")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$project_phase)
print("Garden types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
print("Compost types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost)
print("Compost types & garden types")
table(stacked_raster_values_and_garden_CT_all_seasons_no_nas$compost, stacked_raster_values_and_garden_CT_all_seasons_no_nas$garden_type)
```


```{r}
ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = Local_tree_cover)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(y = Local_tree_cover)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = garden_type, y = garden_size)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = pop_100)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = imperv_100)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = noise_100)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = tree_cover_100)) + 
  geom_boxplot()

ggplot(data = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
       mapping = aes(x = as.factor(project_phase), y = distance_border)) + 
  geom_boxplot()
```

# Dataset of the activity per Station per weekend or weekday
We calculated the activity (nr of photos per species) per station and divided if the photos were taken during the week or during the weekend

```{r weekdays weekends}
#code for separating weekdays and weekends
# transform date variables to correct formats
activity_data <- CT_act_date_formated %>% 
  mutate(date_wday = lubridate::wday(CT_act_date_formated$Date, label = TRUE))%>% 
#binary variable for weekdays or weekends
 dplyr::mutate(weekdays_binary = factor(ifelse(date_wday == "Sa"| date_wday == "So", "0", "1")))
##careful here the name of days depend on the language settings of the computer


#filter by date
P1 <- activity_data %>% filter(Date >= list_date_monthly[[1]][1] & Date <= list_date_monthly[[1]][2])
P2 <- activity_data %>% filter(Date >= list_date_monthly[[2]][1] & Date <= list_date_monthly[[2]][2])
P3 <- activity_data %>% filter(Date >= list_date_monthly[[3]][1] & Date <= list_date_monthly[[3]][2])
P4 <- activity_data %>% filter(Date >= list_date_monthly[[4]][1] & Date <= list_date_monthly[[4]][2])
P5 <- activity_data %>% filter(Date >= list_date_monthly[[5]][1] & Date <= list_date_monthly[[5]][2])

#separating for weekends and weekdays
P1_weekdays <- P1 %>% dplyr::filter(weekdays_binary == 1)
P1_weekends <- P1 %>% dplyr::filter(weekdays_binary == 0)

P2_weekdays <- P2 %>% dplyr::filter(weekdays_binary == 1)
P2_weekends <- P2 %>% dplyr::filter(weekdays_binary == 0)

P3_weekdays <- P3 %>% dplyr::filter(weekdays_binary == 1)
P3_weekends <- P3 %>% dplyr::filter(weekdays_binary == 0)

P4_weekdays <- P4 %>% dplyr::filter(weekdays_binary == 1)
P4_weekends <- P4 %>% dplyr::filter(weekdays_binary == 0)

P5_weekdays <- P5 %>% dplyr::filter(weekdays_binary == 1)
P5_weekends <- P5 %>% dplyr::filter(weekdays_binary == 0)
```

```{r activity function}
#function for counting the number of pictures for each species
activity <- function(species, CT)
{
  CT_species <- CT %>% filter(Species == species)

  Unique_CT <- unique(CT_species$Station)
  l <- list(0)

  for(i in Unique_CT)
    {
      l[[which(Unique_CT == i)]] <- 
      nrow(CT_species %>% filter(Station == i)) 
     #% of pictures taken during the night
      names(l)[which(Unique_CT == i)] <- as.character(i)
       }
   x <- data.frame(unlist(l))
   x <- dplyr::rename(x, activity = unlist.l.)
   x <- x %>% mutate(User_uid = as.numeric(rownames(x)))
   x_covenv <- dplyr::inner_join(x = x,
                                 y = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
                                 by = c("User_uid" = "Station")) 
                #merging with the covenv
   return(x_covenv)

}
```

## Create a table per species per phase/season per weekdays/weekend
```{r table per species per season per weekends/weekdays}
## P1
squirrel_P1_activity_weekdays <- activity("Squirrel", P1_weekdays) %>%
  mutate(species = "Squirrel", weekdays = 1)
squirrel_P1_activity_weekends <- activity("Squirrel", P1_weekends) %>%
  mutate(species = "Squirrel", weekdays = 0)

cat_P1_activity_weekdays <- activity("Cat", P1_weekdays) %>%
  mutate(species = "Cat", weekdays = 1)
cat_P1_activity_weekends <- activity("Cat", P1_weekends) %>%
  mutate(species = "Cat", weekdays = 0)

fox_P1_activity_weekdays <- activity("Red Fox", P1_weekdays) %>%
  mutate(species = "Red Fox", weekdays = 1)
fox_P1_activity_weekends <- activity("Red Fox", P1_weekends) %>%
  mutate(species = "Red Fox", weekdays = 0)

marten_P1_activity_weekdays <- activity("Marten", P1_weekdays) %>%
  mutate(species = "Marten", weekdays = 1)
marten_P1_activity_weekends <- activity("Marten", P1_weekends) %>%
  mutate(species = "Marten", weekdays = 0)

raccoon_P1_activity_weekdays <- activity("Raccoon", P1_weekdays) %>%
  mutate(species = "Raccoon", weekdays = 1)
raccoon_P1_activity_weekends <- activity("Raccoon", P1_weekends) %>%
  mutate(species = "Raccoon", weekdays = 0)

## P2
squirrel_P2_activity_weekdays <- activity("Squirrel", P2_weekdays) %>%
  mutate(species = "Squirrel", weekdays = 1)
squirrel_P2_activity_weekends <- activity("Squirrel", P2_weekends) %>%
  mutate(species = "Squirrel", weekdays = 0)

cat_P2_activity_weekdays <- activity("Cat", P2_weekdays) %>%
  mutate(species = "Cat", weekdays = 1)
cat_P2_activity_weekends <- activity("Cat", P2_weekends) %>%
  mutate(species = "Cat", weekdays = 0)

fox_P2_activity_weekdays <- activity("Red Fox", P2_weekdays) %>%
  mutate(species = "Red Fox", weekdays = 1)
fox_P2_activity_weekends <- activity("Red Fox", P2_weekends) %>%
  mutate(species = "Red Fox", weekdays = 0)

marten_P2_activity_weekdays <- activity("Marten", P2_weekdays) %>%
  mutate(species = "Marten", weekdays = 1)
marten_P2_activity_weekends <- activity("Marten", P2_weekends) %>%
  mutate(species = "Marten", weekdays = 0)

raccoon_P2_activity_weekdays <- activity("Raccoon", P2_weekdays) %>%
  mutate(species = "Raccoon", weekdays = 1)
raccoon_P2_activity_weekends <- activity("Raccoon", P2_weekends) %>%
  mutate(species = "Raccoon", weekdays = 0)

## P3
squirrel_P3_activity_weekdays <- activity("Squirrel", P3_weekdays) %>%
  mutate(species = "Squirrel", weekdays = 1)
squirrel_P3_activity_weekends <- activity("Squirrel", P3_weekends) %>%
  mutate(species = "Squirrel", weekdays = 0)

cat_P3_activity_weekdays <- activity("Cat", P3_weekdays) %>%
  mutate(species = "Cat", weekdays = 1)
cat_P3_activity_weekends <- activity("Cat", P3_weekends) %>%
  mutate(species = "Cat", weekdays = 0)

fox_P3_activity_weekdays <- activity("Red Fox", P3_weekdays) %>%
  mutate(species = "Red Fox", weekdays = 1)
fox_P3_activity_weekends <- activity("Red Fox", P3_weekends) %>%
  mutate(species = "Red Fox", weekdays = 0)

marten_P3_activity_weekdays <- activity("Marten", P3_weekdays) %>%
  mutate(species = "Marten", weekdays = 1)
marten_P3_activity_weekends <- activity("Marten", P3_weekends) %>%
  mutate(species = "Marten", weekdays = 0)

raccoon_P3_activity_weekdays <- activity("Raccoon", P3_weekdays) %>%
  mutate(species = "Raccoon", weekdays = 1)
raccoon_P3_activity_weekends <- activity("Raccoon", P3_weekends) %>%
  mutate(species = "Raccoon", weekdays = 0)

#P4
squirrel_P4_activity_weekdays <- activity("Squirrel", P4_weekdays) %>%
  mutate(species = "Squirrel", weekdays = 1)
squirrel_P4_activity_weekends <- activity("Squirrel", P4_weekends) %>%
  mutate(species = "Squirrel", weekdays = 0)

cat_P4_activity_weekdays <- activity("Cat", P4_weekdays) %>%
  mutate(species = "Cat", weekdays = 1)
cat_P4_activity_weekends <- activity("Cat", P4_weekends) %>%
  mutate(species = "Cat", weekdays = 0)

fox_P4_activity_weekdays <- activity("Red Fox", P4_weekdays) %>%
  mutate(species = "Red Fox", weekdays = 1)
fox_P4_activity_weekends <- activity("Red Fox", P4_weekends) %>%
  mutate(species = "Red Fox", weekdays = 0)

marten_P4_activity_weekdays <- activity("Marten", P4_weekdays) %>%
  mutate(species = "Marten", weekdays = 1)
marten_P4_activity_weekends <- activity("Marten", P4_weekends) %>%
  mutate(species = "Marten", weekdays = 0)

raccoon_P4_activity_weekdays <- activity("Raccoon", P4_weekdays) %>%
  mutate(species = "Raccoon", weekdays = 1)
raccoon_P4_activity_weekends <- activity("Raccoon", P4_weekends) %>%
  mutate(species = "Raccoon", weekdays = 0)

#P5
squirrel_P5_activity_weekdays <- activity("Squirrel", P5_weekdays) %>%
  mutate(species = "Squirrel", weekdays = 1)
squirrel_P5_activity_weekends <- activity("Squirrel", P5_weekends) %>%
  mutate(species = "Squirrel", weekdays = 0)

cat_P5_activity_weekdays <- activity("Cat", P5_weekdays) %>%
  mutate(species = "Cat", weekdays = 1)
cat_P5_activity_weekends <- activity("Cat", P5_weekends) %>%
  mutate(species = "Cat", weekdays = 0)

fox_P5_activity_weekdays <- activity("Red Fox", P5_weekdays) %>%
  mutate(species = "Red Fox", weekdays = 1)
fox_P5_activity_weekends <- activity("Red Fox", P5_weekends) %>%
  mutate(species = "Red Fox", weekdays = 0)

marten_P5_activity_weekdays <- activity("Marten", P5_weekdays) %>%
  mutate(species = "Marten", weekdays = 1)
marten_P5_activity_weekends <- activity("Marten", P5_weekends) %>%
  mutate(species = "Marten", weekdays = 0)

raccoon_P5_activity_weekdays <- activity("Raccoon", P5_weekdays) %>%
  mutate(species = "Raccoon", weekdays = 1)
raccoon_P5_activity_weekends <- activity("Raccoon", P5_weekends) %>%
  mutate(species = "Raccoon", weekdays = 0)

# Combine all data sets
Activity_squirrel_pred_Berlin_all_seasons <- 
  rbind(# P1
    squirrel_P1_activity_weekdays, squirrel_P1_activity_weekends, 
    cat_P1_activity_weekdays,cat_P1_activity_weekends,
    fox_P1_activity_weekdays,fox_P1_activity_weekends,
    marten_P1_activity_weekdays,marten_P1_activity_weekends,
    raccoon_P1_activity_weekdays,raccoon_P1_activity_weekends,
    # P2
    squirrel_P2_activity_weekdays, squirrel_P2_activity_weekends, 
    cat_P2_activity_weekdays, cat_P2_activity_weekends, 
    fox_P2_activity_weekdays, fox_P2_activity_weekends, 
    marten_P2_activity_weekdays, marten_P2_activity_weekends,
    raccoon_P2_activity_weekdays, raccoon_P2_activity_weekends,
    # P3
    squirrel_P3_activity_weekdays, squirrel_P3_activity_weekends,
    cat_P3_activity_weekdays, cat_P3_activity_weekends,
    fox_P3_activity_weekdays, fox_P3_activity_weekends, 
    marten_P3_activity_weekdays, marten_P3_activity_weekends,
    raccoon_P3_activity_weekdays, raccoon_P3_activity_weekends,
    # P4
    squirrel_P4_activity_weekdays, squirrel_P4_activity_weekends,
    cat_P4_activity_weekdays, cat_P4_activity_weekends,
    fox_P4_activity_weekdays, fox_P4_activity_weekends,
    marten_P4_activity_weekdays, marten_P4_activity_weekends,
    raccoon_P4_activity_weekdays, raccoon_P4_activity_weekends,
    # P5
    squirrel_P5_activity_weekdays, squirrel_P5_activity_weekends,
    cat_P5_activity_weekdays, cat_P5_activity_weekends,
    fox_P5_activity_weekdays, fox_P5_activity_weekends,
    marten_P5_activity_weekdays, marten_P5_activity_weekends, 
    raccoon_P5_activity_weekdays, raccoon_P5_activity_weekends)

length(unique(Activity_squirrel_pred_Berlin_all_seasons$User_uid)) #669
```



## Overview
```{r}
# 
table(Activity_squirrel_pred_Berlin_all_seasons$species)

# 
Activity_squirrel_pred_Berlin_all_seasons %>% 
  group_by(species) %>%
  dplyr::summarise(n_pics = sum(activity))

# 
table(Activity_squirrel_pred_Berlin_all_seasons$species, Activity_squirrel_pred_Berlin_all_seasons$project_phase) 

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, mapping = aes(x = species)) + 
  geom_bar() + 
  facet_grid(weekdays ~ .)
# 0 = weekend, 1 = week

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, mapping = aes(x = species)) + 
  geom_bar() + 
  facet_grid(garden_type ~ .)

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, mapping = aes(x = species)) + 
  geom_bar() + 
  facet_grid(compost ~ .)

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, 
       mapping = aes(x = species, y = Local_tree_cover)) + 
  geom_boxplot()

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, 
       mapping = aes(x = species, y = pop_100)) + 
  geom_boxplot()

ggplot(data = Activity_squirrel_pred_Berlin_all_seasons, 
       mapping = aes(x = species, y = imperv_100)) + 
  geom_boxplot()
```


# Squirrels only
We build a data set only for the squirrels.
```{r squirrel data set}
# squirrels_CT <- CT_act_date_formated[CT_act_date_formated$Species == "Squirrel",]
# # add a column for the hour of the day
# squirrels_CT$hour <- hour(squirrels_CT$Time)
```

# Diurnality
Squirrels where active between 5am and 7pm. So we will filter our data for the time between 5am-7pm for the whole month divided by weekdays and weekends
```{r diurnality function}
# #function for counting the number of pictures for each species
# diurnality <- function(species, CT) # one has to insert the species and the data set for the filtering
# {
#   CT_species <- CT %>% filter(Species == species) # 
# 
#   Unique_CT <- unique(CT_species$Station)
#   l <- list(0)
#   k <- list(0)
# 
#   for(i in Unique_CT)
#     { #% of pictures taken during the day
#       l[[which(Unique_CT == i)]] <- 
#       (nrow(CT_species %>% filter(Station == i) %>% dplyr::filter(Time >= hms("05:00:00") 
#                                 & Time <= hms("19:00:00"))))/nrow(CT_species %>%
#                            filter(Station == i)) 
#       names(l)[which(Unique_CT == i)] <- as.character(i)
#       
#       #number of pictures taken during the day
#       k[[which(Unique_CT == i)]] <- 
#       (nrow(CT_species %>% filter(Station == i) %>% dplyr::filter(Time >= hms("05:00:00") 
#                                 & Time <= hms("19:00:00")))) 
#       names(k)[which(Unique_CT == i)] <- as.character(i)
# 
#        }
#    x <- data.frame(unlist(l))
#    x <- dplyr::rename(x, diurnality = unlist.l.)
#    x <- x %>% mutate(User_uid = as.numeric(rownames(x)))
#    x_covenv <- dplyr::inner_join(x = x,
#                                  y = stacked_raster_values_and_garden_CT_all_seasons_no_nas, 
#                                  by = c("User_uid" = "Station")) #merging with the covenv
# 
#    y <- data.frame(unlist(k))
#    y <- dplyr::rename(y, nbr_pictures_day = unlist.k.)
#    y <- y %>% mutate(User_uid = as.numeric(rownames(y)))
#    y_covenv <- dplyr::inner_join(x = y,
#                                  y = x_covenv) #merging with the covenv
#    return(y_covenv)
#    
# }
```


## Create a table per species per season per weekdays/weekend
```{r diurnality table}
# #P1
# squirrel_P1_diurnality_weekdays <- diurnality("Eichhörnchen", P1_weekdays) %>%
#   mutate(species = "Squirrel", weekdays = 1)
# squirrel_P1_diurnality_weekends <- diurnality("Eichhörnchen", P1_weekends) %>%
#   mutate(species = "Squirrel", weekdays = 0)
# 
# cat_P1_diurnality_weekdays <- diurnality("cat", P1_weekdays) %>%
#   mutate(species = "Cat", weekdays = 1)
# cat_P1_diurnality_weekends <- diurnality("cat", P1_weekends) %>%
#   mutate(species = "Cat", weekdays = 0)
# 
# fox_P1_diurnality_weekdays <- diurnality("Rotfuchs", P1_weekdays) %>%
#   mutate(species = "Fox", weekdays = 1)
# fox_P1_diurnality_weekends <- diurnality("Rotfuchs", P1_weekends) %>%
#   mutate(species = "Fox", weekdays = 0)
# 
# marten_P1_diurnality_weekdays <- diurnality("Marder_(Baum-und_Steinmarder)", P1_weekdays) %>%
#   mutate(species = "Marten", weekdays = 1)
# marten_P1_diurnality_weekends <- diurnality("Marder_(Baum-und_Steinmarder)", P1_weekends) %>%
#   mutate(species = "Marten", weekdays = 0)
# 
# raccoon_P1_diurnality_weekdays <- diurnality("Waschbär", P1_weekdays) %>%
#   mutate(species = "Raccoon", weekdays = 1)
# raccoon_P1_diurnality_weekends <- diurnality("Waschbär", P1_weekends) %>%
#   mutate(species = "Raccoon", weekdays = 0)
# 
# #P2
# squirrel_P2_diurnality_weekdays <- diurnality("Eichhörnchen", P2_weekdays) %>%
#   mutate(species = "Squirrel", weekdays = 1)
# squirrel_P2_diurnality_weekends <- diurnality("Eichhörnchen", P2_weekends) %>%
#   mutate(species = "Squirrel", weekdays = 0)
# 
# cat_P2_diurnality_weekdays <- diurnality("cat", P2_weekdays) %>%
#   mutate(species = "Cat", weekdays = 1)
# cat_P2_diurnality_weekends <- diurnality("cat", P2_weekends) %>%
#   mutate(species = "Cat", weekdays = 0)
# 
# fox_P2_diurnality_weekdays <- diurnality("Rotfuchs", P2_weekdays) %>%
#   mutate(species = "Fox", weekdays = 1)
# fox_P2_diurnality_weekends <- diurnality("Rotfuchs", P2_weekends) %>%
#   mutate(species = "Fox", weekdays = 0)
# 
# marten_P2_diurnality_weekdays <- diurnality("Marder_(Baum-und_Steinmarder)", P2_weekdays) %>%
#   mutate(species = "Marten", weekdays = 1)
# marten_P2_diurnality_weekends <- diurnality("Marder_(Baum-und_Steinmarder)", P2_weekends) %>%
#   mutate(species = "Marten", weekdays = 0)
# 
# raccoon_P2_diurnality_weekdays <- diurnality("Waschbär", P2_weekdays) %>%
#   mutate(species = "Raccoon", weekdays = 1)
# raccoon_P2_diurnality_weekends <- diurnality("Waschbär", P2_weekends) %>%
#   mutate(species = "Raccoon", weekdays = 0)
# 
# #P3
# squirrel_P3_diurnality_weekdays <- diurnality("Eichhörnchen", P3_weekdays) %>%
#   mutate(species = "Squirrel", weekdays = 1)
# squirrel_P3_diurnality_weekends <- diurnality("Eichhörnchen", P3_weekends) %>%
#   mutate(species = "Squirrel", weekdays = 0)
# 
# cat_P3_diurnality_weekdays <- diurnality("cat", P3_weekdays) %>%
#   mutate(species = "Cat", weekdays = 1)
# cat_P3_diurnality_weekends <- diurnality("cat", P3_weekends) %>%
#   mutate(species = "Cat", weekdays = 0)
# 
# fox_P3_diurnality_weekdays <- diurnality("Rotfuchs", P3_weekdays) %>%
#   mutate(species = "Fox", weekdays = 1)
# fox_P3_diurnality_weekends <- diurnality("Rotfuchs", P3_weekends) %>%
#   mutate(species = "Fox", weekdays = 0)
# 
# marten_P3_diurnality_weekdays <- diurnality("Marder_(Baum-und_Steinmarder)", P3_weekdays) %>%
#   mutate(species = "Marten", weekdays = 1)
# marten_P3_diurnality_weekends <- diurnality("Marder_(Baum-und_Steinmarder)", P3_weekends) %>%
#   mutate(species = "Marten", weekdays = 0)
# 
# raccoon_P3_diurnality_weekdays <- diurnality("Waschbär", P3_weekdays) %>%
#   mutate(species = "Raccoon", weekdays = 1)
# raccoon_P3_diurnality_weekends <- diurnality("Waschbär", P3_weekends) %>%
#   mutate(species = "Raccoon", weekdays = 0)
# 
# #P4
# squirrel_P4_diurnality_weekdays <- diurnality("Eichhörnchen", P4_weekdays) %>%
#   mutate(species = "Squirrel", weekdays = 1)
# squirrel_P4_diurnality_weekends <- diurnality("Eichhörnchen", P4_weekends) %>%
#   mutate(species = "Squirrel", weekdays = 0)
# 
# cat_P4_diurnality_weekdays <- diurnality("cat", P4_weekdays) %>%
#   mutate(species = "Cat", weekdays = 1)
# cat_P4_diurnality_weekends <- diurnality("cat", P4_weekends) %>%
#   mutate(species = "Cat", weekdays = 0)
# 
# fox_P4_diurnality_weekdays <- diurnality("Rotfuchs", P4_weekdays) %>%
#   mutate(species = "Fox", weekdays = 1)
# fox_P4_diurnality_weekends <- diurnality("Rotfuchs", P4_weekends) %>%
#   mutate(species = "Fox", weekdays = 0)
# 
# marten_P4_diurnality_weekdays <- diurnality("Marder_(Baum-und_Steinmarder)", P4_weekdays) %>%
#   mutate(species = "Marten", weekdays = 1)
# marten_P4_diurnality_weekends <- diurnality("Marder_(Baum-und_Steinmarder)", P4_weekends) %>%
#   mutate(species = "Marten", weekdays = 0)
# 
# raccoon_P4_diurnality_weekdays <- diurnality("Waschbär", P4_weekdays) %>%
#   mutate(species = "Raccoon", weekdays = 1)
# raccoon_P4_diurnality_weekends <- diurnality("Waschbär", P4_weekends) %>%
#   mutate(species = "Raccoon", weekdays = 0)
# 
# #P5
# squirrel_P5_diurnality_weekdays <- diurnality("Eichhörnchen", P5_weekdays) %>%
#   mutate(species = "Squirrel", weekdays = 1)
# squirrel_P5_diurnality_weekends <- diurnality("Eichhörnchen", P5_weekends) %>%
#   mutate(species = "Squirrel", weekdays = 0)
# 
# cat_P5_diurnality_weekdays <- diurnality("cat", P5_weekdays) %>%
#   mutate(species = "Cat", weekdays = 1)
# cat_P5_diurnality_weekends <- diurnality("cat", P5_weekends) %>%
#   mutate(species = "Cat", weekdays = 0)
# 
# fox_P5_diurnality_weekdays <- diurnality("Rotfuchs", P5_weekdays) %>%
#   mutate(species = "Fox", weekdays = 1)
# fox_P5_diurnality_weekends <- diurnality("Rotfuchs", P5_weekends) %>%
#   mutate(species = "Fox", weekdays = 0)
# 
# marten_P5_diurnality_weekdays <- diurnality("Marder_(Baum-und_Steinmarder)", P5_weekdays) %>%
#   mutate(species = "Marten", weekdays = 1)
# marten_P5_diurnality_weekends <- diurnality("Marder_(Baum-und_Steinmarder)", P5_weekends) %>%
#   mutate(species = "Marten", weekdays = 0)
# 
# raccoon_P5_diurnality_weekdays <- diurnality("Waschbär", P5_weekdays) %>%
#   mutate(species = "Raccoon", weekdays = 1)
# raccoon_P5_diurnality_weekends <- diurnality("Waschbär", P5_weekends) %>%
#   mutate(species = "Raccoon", weekdays = 0)
# 
# # Combine the data sets
# diurnality_predprey_Berlin_all_seasons <- 
#   rbind( # P1
#     squirrel_P1_diurnality_weekdays, squirrel_P1_diurnality_weekends,
#     cat_P1_diurnality_weekdays, cat_P1_diurnality_weekends,
#     fox_P1_diurnality_weekdays, fox_P1_diurnality_weekends, 
#     marten_P1_diurnality_weekdays, marten_P1_diurnality_weekends,
#     raccoon_P1_diurnality_weekdays, raccoon_P1_diurnality_weekends,
#     # P2
#     squirrel_P2_diurnality_weekdays, squirrel_P2_diurnality_weekends,
#     cat_P2_diurnality_weekdays, cat_P2_diurnality_weekends,
#     fox_P2_diurnality_weekdays, fox_P2_diurnality_weekends,
#     marten_P2_diurnality_weekdays, marten_P2_diurnality_weekends, 
#     raccoon_P2_diurnality_weekdays, raccoon_P2_diurnality_weekends,
#     # P3
#     squirrel_P3_diurnality_weekdays, squirrel_P3_diurnality_weekends,
#     cat_P3_diurnality_weekdays, cat_P3_diurnality_weekends,
#     fox_P3_diurnality_weekdays, fox_P3_diurnality_weekends, 
#     marten_P3_diurnality_weekdays, marten_P3_diurnality_weekends,
#     raccoon_P3_diurnality_weekdays, raccoon_P3_diurnality_weekends,
#     # P4
#     squirrel_P4_diurnality_weekdays, squirrel_P4_diurnality_weekends,
#     cat_P4_diurnality_weekdays, cat_P4_diurnality_weekends,
#     fox_P4_diurnality_weekdays, fox_P4_diurnality_weekends, 
#     marten_P4_diurnality_weekdays, marten_P4_diurnality_weekends,
#     raccoon_P4_diurnality_weekdays, raccoon_P4_diurnality_weekends,
#     # P5
#     squirrel_P5_diurnality_weekdays, squirrel_P5_diurnality_weekends,
#     cat_P5_diurnality_weekdays, cat_P5_diurnality_weekends,
#     fox_P5_diurnality_weekdays, fox_P5_diurnality_weekends,
#     marten_P5_diurnality_weekdays, marten_P5_diurnality_weekends, 
#     raccoon_P5_diurnality_weekdays, raccoon_P5_diurnality_weekends)
# 
# length(unique(diurnality_predprey_Berlin_all_seasons$User_uid))
```

Hint: it is fine that the number of rows in the datasets for activity and diurnality are the same. But the number of pictures per day per station is different

# Save data
```{r}
# CT_act_date_formated
# saveRDS(object = CT_act_date_formated,
#         file = here::here("output", "data-proc", "all_seasons",
#                           "CT_act_date_proc_20221117.RDS"))
# 
# # stacked_raster_values_and_garden_CT_all_seasons_no_nas
# saveRDS(object = stacked_raster_values_and_garden_CT_all_seasons_no_nas,
#         file = here::here("output", "data-proc", "all_seasons",
#                           "stacked_raster_values_and_garden_CT_all_seasons_no_nas_proc_20221117.RDS"))
# 
# # Activity_squirrel_pred_Berlin_all_seasons
# saveRDS(object = Activity_squirrel_pred_Berlin_all_seasons,
#         file = here::here("output", "data-proc", "all_seasons",
#                           "Activity_squirrel_pred_Berlin_all_seasons_20221117.RDS"))
# 
# 
# # squirrels_CT
# saveRDS(object = squirrels_CT,
#         file = here::here("output", "data-proc", "all_seasons",
#                           "squirrels_CT_20221117.RDS"))
#
#
# # Diurnality
# # saveRDS(object = diurnality_predprey_Berlin_all_seasons,
# #         file = here::here("output", "data-proc", "all_seasons",
# #                           "diurnality_predprey_Berlin_all_seasons_20220802.RDS"))
```

***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
