---
title: "Squirrel activity: Preparation of the environmental data and correlation test" ## name of your project and analysis step
description: |
    The aim of the study is to investigate the influence of altered environmental urban parameters and direct human disturbance expressed by the lockdown together with animal predator risk parameters on the general activity of squirrels
author:
    - name: "Sinah Drenske"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-2247-6507
    - name: "Julie Louvrier"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-1252-1746
    - name: "Marius Grabow"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-0702-9642
    - name: "Conny Landgraf"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      #orcid_id: 0000-0000-0000-0000
    - name: "Stephanie Kramer-Schadt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-9269-4446
    - name: "Aimara Planillo"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0001-6763-9923
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      ## styling of code
        code_folding: TRUE  ## if `true` you can expand and shrink code chunks
        toc: true            ## if `true` adds a table of content
        toc_depth: 2         ## level to be displayed in the table of content
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

* **Research question:** Which risk effects increase or decrease the overall activity of red squirrels in urban gardens?  
* **Study area:** Berlin 2019-2020 
* **Data:** Detection histories of squirrels, martens and cats from 4 seasons (spring 2019, autumn 2019, spring 2020, autumn 2020), already filtered as in Louvrier et al. 2021 + environmental information on camera stations.

# Setup

```{r packages}
#remotes::install_github("EcoDynIZW/d6")
d6::simple_load(c("ggpubr",
                  "raster", 
                  "sf",
                  "tidyverse"
)) 
```


# Data
```{r data}
# City border
berlin <- st_read(here::here("data-raw",
                             "geo-raw",
                             "berlin_city_border_25833.gpkg"), crs = 25833) %>% 
  st_union() %>% 
  st_transform(crs = 3035) %>% 
  st_cast(to = 'LINESTRING')

### read layer with borders of the districts of Berlin NOT WORKING ----
# Combine them to get the city border

# berlin <- 
#   st_read(here::here("data-raw",
#                      "geo-raw",
#                      "districs_berlin_2022_poly_03035_gpkg",
#                      "districs_berlin_2022_poly_03035.gpkg"), crs = 3035) %>%
#   st_union() %>%
#   st_buffer(100) %>%
#   st_crop(berlin) %>%
#   st_cast(to = 'LINESTRING')
# berlin

### read all environmental raster data ----
## Imperviousness 2018
imperviousness_2018 <-
  raster(here::here("data-raw",
                    "geo-raw",
                    "imperviousness_berlin_copernicus_raster_10m_2018_3035",
                    "imperviousness_berlin_copernicus_raster_10m_2018_3035.tif"
  )) %>%
  focal(w = matrix(1,nrow = 11,ncol = 11),fun = mean, na.rm = TRUE)

crs(imperviousness_2018) <- crs("+init=epsg:3035")

## Light pollution
light_pollution_2021 <-
  raster(here::here("data-raw",
                    "geo-raw",
                    "light-pollution_berlin_2021_10m_03035_tif",
                    "light-pollution_berlin_2021_10m_03035.tif"
  ))

## Noise pollution
noise_pollution_2017 <-
  raster(here::here("data-raw",
                    "geo-raw",
                    "noise-day-night_berlin_2017_10m_03035_tif",
                    "noise-day-night_berlin_2017_10m_03035.tif"
  ))

## Population density 2019
population_density_2019 <-
  raster(here::here("data-raw",
                    "geo-raw",
                    "population-density_berlin_2019_10m_03035_tif",
                    "population-density_berlin_2019_10m_03035.tif"
  ))

## Tree cover density
tree_cover_density_2018 <-
  raster(here::here("data-raw",
                    "geo-raw",
                    "tree-cover-density_berlin_2018_10m_03035_tif",
                    "tree-cover-density_berlin_2018_10m_03035.tif"
  ))


focal_tree_cover_density_2018 <- focal(tree_cover_density_2018, w = matrix(1,11,11), fun = mean, na.rm = TRUE)

#writeRaster(focal_tree_cover_density_2018, "./output/geo-proc/tree_cover_2018_focalmean_3035.tif")

```
```{r}
summary(focal_tree_cover_density_2018)
summary(tree_cover_density_2018)
summary(imperviousness_2018)
summary(population_density_2019)
summary(light_pollution_2021)
summary(noise_pollution_2017)
```


Plot all layers
```{r}
plot(berlin)
plot(imperviousness_2018)
plot(light_pollution_2021)
plot(noise_pollution_2017)
plot(population_density_2019)
plot(tree_cover_density_2018)
plot(focal_tree_cover_density_2018)
```


# Combine urban data with garden data
```{r extract data}
ct_locations <- readRDS(here::here("output",
                                   "data-proc",
                                   "01_overall_activity",
                                   "stacked_raster_values_and_garden_CT_all_seasons_no_nas_proc_20230305.RDS"))

ct_spatial <- st_as_sf(ct_locations,coords = c("Long","Lat"),remove = F, crs = 32633) %>%
  st_transform(crs = 3035)


#### extract covariates ----
# imperviousness
cov_imperviousness_2018 <- raster::extract(x = imperviousness_2018, y = ct_spatial) %>%
  data.frame()

cov_imperviousness_2018_2 <- raster::extract(x = imperviousness_2018, y = ct_spatial, fun = mean) %>%
  data.frame()

colnames(cov_imperviousness_2018) <- "imperviousness_2018"

# light pollution
cov_light_2021 <- raster::extract(x = light_pollution_2021, y = ct_spatial) %>%
  data.frame()

cov_light_2021_2 <- raster::extract(x = light_pollution_2021, y = ct_spatial, fun = mean) %>%
  data.frame()

colnames(cov_light_2021) <- "light_2021"

# noise pollution
cov_noise_2017 <- raster::extract(x = noise_pollution_2017, y = ct_spatial) %>%
  data.frame()

colnames(cov_noise_2017) <- "noise_2017"


# population density
cov_pop_2019 <- terra::extract(x = population_density_2019, y = ct_spatial) %>%
  data.frame()

cov_pop_2019_2 <- raster::extract(x = population_density_2019, y = ct_spatial, fun = mean, na.rm = TRUE) %>%
  data.frame()

colnames(cov_pop_2019) <- "pop_2019"

# Tree cover density
cov_tree_cover_2018 <- raster::extract(x = focal_tree_cover_density_2018, y = ct_spatial) %>%
  data.frame()

colnames(cov_tree_cover_2018) <- "tree_cover_2018"

###################

# distance to border
dist_border <- st_distance(ct_spatial, berlin)

colnames(dist_border) <- "distance_to_border"
range(dist_border)

# bind data
ct_cov <- cbind(ct_spatial,
                cov_imperviousness_2018, 
                cov_light_2021, 
                cov_noise_2017, 
                cov_pop_2019, 
                cov_tree_cover_2018, 
                dist_border
) %>%
  st_drop_geometry() %>%
  as_tibble()

#dplyr::select(-c(10,12,13,15:18)) # only to compare them
#dplyr::select(-c(pop_100,distance_border,imperv_100))

ct_cov$distance_to_border <- as.numeric(ct_cov$distance_to_border)
```


## Save data

```{r save data}
# ct_cov_save <- ct_cov %>%
#   dplyr::select(Station, project_phase, Season, lockdown,
#                 garden_type, garden_size, Local_tree_cover, fence_height, compost,
#                 dogs_binary, cats_binary, trees_of_interest, Lat, Long, inside,
#                 imperviousness_2018, noise_2017, pop_2019, tree_cover_2018, distance_to_border)
# saveRDS(ct_cov_save,here::here("output",
#                                "data-proc",
#                                "01_overall_activity",
#                                "ct_focal_covariates_100_20230305.RDS"))
```


# Plots
## Imperviousness
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = imperv_100)) + 
  geom_point() + 
  labs(title = "Imperviousness")
ggplot(data = ct_cov, mapping = aes(x = Station, y = imperviousness_2018)) + 
  geom_point() + 
  labs(title = "New Imperviousness")
ggplot(data = ct_cov, mapping = aes(x = imperv_100, y = imperviousness_2018)) + 
  geom_point() + 
  labs(title = "comparison of imperviousness values")
```

## Light pollution
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = light_2021)) + 
  geom_point() + 
  labs(title = "New Light")
```


## Noise pollution
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = noise_100)) + 
  geom_point() + 
  labs(title = "Noise")
ggplot(data = ct_cov, mapping = aes(x = Station, y = noise_2017)) + 
  geom_point() + 
  labs(title = "New Noise")
ggplot(data = ct_cov, mapping = aes(x = noise_100, y = noise_2017)) + 
  geom_point() + 
  labs(title = "comparison of noise values")
```


## Population density
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = pop_100)) + 
  geom_point() + 
  ylim(0, 700) + 
  xlim(0, 700) + 
  labs(title = "Population density")

ggplot(data = ct_cov, mapping = aes(x = Station, y = pop_2019)) + 
  geom_point() + 
  ylim(0, 700) + 
  xlim(0, 700) + 
  labs(title = "New Population density")

ggplot(data = ct_cov, mapping = aes(x = pop_100, y = pop_2019)) + 
  geom_point() + 
  ylim(0, 700) + 
  xlim(0, 700) + 
  labs(title = "Comparison of population density values")
```

```{r}
table(is.na(ct_cov$pop_100), useNA = "always")
table(is.na(ct_cov$pop_2019), useNA = "always") #113 NaN
#table(ct_cov$population_density_2019, useNA = "always")
```

## Tree cover density
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = tree_cover_100)) + 
  geom_point() + 
  ylim(0, 100) +
  xlim(0, 100) +
  labs(title = "Tree cover density")

ggplot(data = ct_cov, mapping = aes(x = Station, y = tree_cover_2018)) + 
  geom_point() + 
  ylim(0, 100) + 
  xlim(0, 100) + 
  labs(title = "New Tree cover density")

ggplot(data = ct_cov, mapping = aes(x = tree_cover_100, y = tree_cover_2018)) + 
  geom_point() + 
  ylim(0, 100) + 
  xlim(0, 100) + 
  labs(title = "Comparison of Tree cover density values")
```

## Distance to border
```{r}
ggplot(data = ct_cov, mapping = aes(x = Station, y = distance_border)) + 
  geom_point() + 
  ylim(0, 20000) + 
  labs(title = "Distance to border")

ggplot(data = ct_cov, mapping = aes(x = Station, y = distance_to_border)) + 
  geom_point() + 
  ylim(0, 20000) + 
  labs(title = "Distance to border New")

ggplot(data = ct_cov, mapping = aes(x = distance_border, y = distance_to_border)) + 
  geom_point() + 
  ylim(0, 15000) + 
  xlim(0, 15000) +
  labs(title = "Comparison of disance to border values")
```

# Correlation plots
```{r correlation at ct locations, fig.height=9, fig.width=12}
cov <- ct_cov %>%
  dplyr::select(garden_size,
                Local_tree_cover,
                fence_height,
                dist_water_100,
                imperviousness_2018,
                light_2021,
                noise_2017, 
                pop_2019,
                tree_cover_2018,
                distance_to_border                
                ) %>%
  mutate(distance_to_border = as.numeric(distance_to_border)) %>%
  st_drop_geometry()



cor_loc <- cor(cov, use = "complete.obs") %>%
  data.frame() %>%
  as.matrix()

melted_cor_loc <- reshape2::melt(cor_loc)
```

```{r}
melted_cor_loc <- melted_cor_loc %>%
  mutate(Var1 = recode(Var1, garden_size = "garden size", 
                       Local_tree_cover = "local tree cover", 
                       fence_height = "fence height", 
                       dist_water_100 = "distance to water bodies", 
                       imperviousness_2018 = "imperviousness", 
                       light_2021 = "light pollution", 
                       noise_2017 = "noise levels", 
                       pop_2019 = "human population density", 
                       tree_cover_2018 = "tree cover density", 
                       distance_to_border = "distance to city border"), 
         Var2 = recode(Var2, garden_size = "garden size", 
                       Local_tree_cover = "local tree cover", 
                       fence_height = "fence height", 
                       dist_water_100 = "distance to water bodies", 
                       imperviousness_2018 = "imperviousness", 
                       light_2021 = "light pollution", 
                       noise_2017 = "noise levels", 
                       pop_2019 = "human population density", 
                       tree_cover_2018 = "tree cover density", 
                       distance_to_border = "distance to city border"))
```



```{r correlation at ct locations, fig.height=9, fig.width=12}
ggplot(data = melted_cor_loc, mapping = aes(x = Var2, y = forcats::fct_rev(Var1), fill = value)) +
  geom_tile() +
  geom_text(aes(
    label = format(round(value, 2), nsmall = 2),
    color = abs(value) < .75
  )) +
  coord_fixed(expand = F) +
  scale_color_manual(values = c("white", "black"),
                     guide = "none") +
  scale_fill_distiller(
    palette = "RdBu", na.value = "white",
    direction = 1, limits = c(-1, 1), name = "Pearson\nCorrelation"
  ) +
  labs(x = NULL, y = NULL) + 
  scale_x_discrete(position = "top") +
  theme_pubr() + 
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        axis.text.x = element_text(angle = 45, hjust = 0),
        legend.position = "right",
        legend.key.size = unit(1.2,"cm"),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20)) + 
  labs_pubr(base_family = "Zilla Slab", base_size = 15) + 
  font(object = "xy.text", family = "Roboto", size = 11)


# ggsave(here::here("plots", 
#                   "01_environmental_variables", 
#                   "ct_correlation_20230305.png"), 
#        width = 12, 
#        height = 9)

# Light correlates with imperviousness, population density and distance to border. It is not used for further analysis.
# Tree cover and imperviousness are highly correlated. We build separate models for both of them. 
# Distance to water is not of interest and is not used for further analysis. 
```


```{r correlation at ct locations old and new values}
cov <- ct_cov %>%
  dplyr::select(garden_size,
                Local_tree_cover,
                fence_height,
                pop_100,
                dist_water_100,
                imperv_100,
                noise_100,
                tree_cover_100,
                distance_border,
                imperviousness_2018,
                light_2021,
                noise_2017, 
                pop_2019,
                tree_cover_2018,
                distance_to_border                
                ) %>%
  mutate(distance_to_border = as.numeric(distance_to_border)) %>%
  st_drop_geometry()



cor_loc <- cor(cov, use = "complete.obs") %>%
  data.frame() %>%
  as.matrix()

melted_cor_loc <- reshape2::melt(cor_loc)

ggplot(data = melted_cor_loc, aes(x = Var2, y = forcats::fct_rev(Var1), fill = value)) +
  geom_tile() +
  geom_text(aes(
    label = format(round(value, 2), nsmall = 2),
    color = abs(value) < .75
  )) +
  coord_fixed(expand = F) +
  scale_color_manual(values = c("white", "black"),
                     guide = "none") +
  scale_fill_distiller(
    palette = "RdBu", na.value = "white",
    direction = 1, limits = c(-1, 1)
  ) +
  labs(x = NULL, y = NULL) + scale_x_discrete(position = "top") +
  theme(panel.border = element_rect(color = NA, fill = NA),
        axis.text.x = element_text(angle = 45, hjust = 0,size = 12),
        axis.text.y = element_text(size = 12),
        legend.key.size = unit(1.2,"cm"),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 20))


#ggsave(here::here("plots", "01_environmental_variables", "ct_correlation_old_new_values.png"), width = 12, height = 9)

```

```{r correlation of full raster, eval=FALSE, echo=TRUE}
# cor<-as.data.frame(layerStats(raster_stack,stat="pearson",na.rm = T))
# colnames(cor)<-rownames(cor)
# cor<-as.matrix(cor[,1:10])
# cor[cor>=1]=1;cor[upper.tri(cor)]<-NA
# 
# melted_cor<-reshape2::melt(cor)
# 
# ggplot(data = melted_cor, aes(x=Var2, y=Var1, fill=value)) +
#   geom_tile() +
#   geom_text(aes(
#     label = format(round(value, 2), nsmall = 2),
#     color = abs(value) < .75
#   )) +
#   coord_fixed(expand = FALSE) +
#   scale_color_manual(values = c("white", "black"),
#                      guide = "none") +
#   scale_fill_distiller(
#     palette = "RdBu", na.value = "white",
#     direction = 1, limits = c(-1, 1)
#   ) +
#   labs(x = NULL, y = NULL) + scale_x_discrete(position = "top")+
#   theme(panel.border = element_rect(color = NA, fill = NA),
#         legend.position = c(.95, .4),
#         axis.text.x = element_text(angle = 45, hjust=0,size = 15),
#         axis.text.y = element_text(size = 15),
#         legend.key.size = unit(1.2,"cm"),
#         legend.text = element_text(size = 15),
#         legend.title = element_text(size = 20))
# 
# ggsave(here("plots","raster_correlation.png"),width = 12, height = 9)
```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
