---
title: "Your Project: Data Preparation" ## name of your project and analysis step
description: |
    The aim of this study is...
author:
    ## author information; single arguemnts can be deleted if not needed
    - name: "John Smith"
      url: https://izw-berlin.de/en/john-smith-en.html  
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0000-0000-0000
    - name: "Jane Doe"
      url: https://janedoe.com
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
    ## add more authors with the same intendation and styling if needed 
    ## a new author always starts with a hyphen!
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      ## styling of code
        code_folding: false  ## if `true` you can expand and shrink code chunks
        toc: true            ## if `true` adds a table of content
        toc_depth: 2         ## level to be displayed in the table of content
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

* **Research question:**
* **Study area:**
* **Data:** 


# Setup
## Packages
```{r packages}
## for non-CRAN packages please keep install instruction
## but commented so it is not run each time, e.g.
# devtools::install_github("EcoDynIZW/template")

## libraries used in this script
## please add ALL LIBRARIES NEEDED HERE
## please remove libraries from the list that are not needed anymore 
## at a later stage
package.list=c(#"camtrapR",
               #"camtrapRdeluxe",
               #"dplyr",
               #"evaluate",
               #"gdata",
               "here",
               "hms",
               #"janitor",
               #"lubridate",
               "magrittr",
               #"maptools",
               #"optimbase",
               #"plyr",
               #"raster",
               #"readxl",
               #"rgdal",
               #"rgeos",
               #"rjags",
               #"rlecuyer",
               #"sf",
               #"showtext",
               #"snowfall",
               #"sp",
               #"stringr",
               "tidyverse"
               )

for (package in package.list) {
  if (!require(package, character.only=T, quietly=T)) {
    install.packages(package)
    library(package, character.only=T)
  }
}

```


## Data

```{r data}
##Camera Traps detection histories
#loading the environmental variables and using only the user IDs that are within the cov table
stacked_raster_values_and_garden_CT_all_seasons_no_nas <- readRDS(here::here("data-raw", "r-raw", "stacked_raster_values_and_garden_CT_all_seasons_allcovs_Renamed2022_01_19.RDS"))

#already formatted and filtered camera trap data with a delta of 30 mins
CT_act_date_formated_delta30 <- readRDS(here::here("data-raw", "r-raw","CT_act_allspecies_NoDelta_filtered2022_01_19.RDS"))
```

# Calculate the time intervals between last detections of the primary species (A) and first detection of the secondary species (B) 
## Preparation of the dataset: Taking out pictures between 7pm and 5am
```{r}
CT_act_day <- CT_act_date_formated_delta30

#extract the hours between 5am and 6pm, 
medium_day <- CT_act_day %>% dplyr::filter(Time >= hms::as_hms("05:00:00"), 
                             Time <= hms::as_hms("19:00:00"))
table(medium_day$Species)
```

### Save output
```{r}
# #saving the output
# saveRDS(object = medium_day, 
#         file = here::here("output", "data-proc", "temporal_proc", 
#                           paste0("medium_day_",gsub(pattern = "-", replacement = "", x = Sys.Date()),".RDS")))
```

##Calculate the temporal difference between each species 
```{r}
#a bit of formating 
data_interest <- medium_day
data_interest %<>%
  mutate(Species = as.factor(Species), 
         Station = as.integer(Station))

data_interest <- as.data.frame(data_interest)

# Extracting the IDs of the CT that detected species of interest
id_CT <- unique(data_interest$Station)

#list of species of interest 
species_interest <- c("Eichhörnchen", "cat", "Waschbär","Rotfuchs", "Marder_(Baum-und_Steinmarder)")
```

### Function to calculate the time interval
```{r}
### Original --------------------------------------------------------
# calculate_delta <- function(species)
#   {
#   #empty list 
#   delta_species <- list(0)
#   ###loop starts here
#   
#   for(j in id_CT)
#     {
#     k = which(id_CT == j)
#     #take the CT by its id 
#     B <- data_interest %>% filter(Station == j)
#   
#     #order it by date and time
#     B_ordered <- B %>% arrange(DateTimeOriginal)
# 
#     #delta is going to contain the calculated difference of time between species A and B for each row of the detections of the CT
#     #but only if the two species from row i and i+1 are in the specific order
#     #if the combination of the species names between the row i and i + 1 is equal to the names of the species of interest     stuck togetehr then we calcutalte difftime between the two lines,  otherwise, no
#   
#     delta <- rep(NA, nrow(B_ordered))
#     for(i in 1: (nrow(B_ordered)))
#       {
#       if (paste(B_ordered[c(i:(i+1)),"Species"], collapse ="") == paste(species, collapse=""))
#         { 
#         diff <- difftime(B_ordered[i,"DateTimeOriginal"], B_ordered[i+1,"DateTimeOriginal"])
#         if (diff < - 12)
#           { 
#           delta[i] <- 0 #if the time difference is more than 12 hours then we set it back to zero because it means too                             much time has spent
#           }
#         if (diff >= -12)
#           {
#           delta[i] <- diff
#           }
#         }
#       }
#   
#     delta_species[[k]] <- delta
#     names(delta_species)[k] <- as.character(j)
#   
#     }
#   return(delta_species)
# 
#   }
```

```{r}
#### TEST ####
##############
##############

# 1st function: for loop 1 take out pics of species of interest per station and order them by date and time
# 2nd function:  calculate the time differences

calculate_delta <- function(species)
 {
  # print(paste0("Start Time ", Sys.time()))
  # start.time <- Sys.time()

  #empty list 
  delta_species <- list(0)
  ###loop starts here
  
  # numberCT: each element of station ID
  for(numberCT in id_CT) 
    {
    #print(paste0("j ", j))
    #numberEle
    numberEle <- which(id_CT == numberCT) 
    #print(paste0("k ", k))
    
    #take the CT by its id, und filter alle Fotos der species of interest pro station/CT 
    Pics_CT <- data_interest %>% filter(Station == numberCT)
  
    #order it by date and time (maybe not necessary, but just in case there is something in the wrong order)
    Pics_CT_ordered <- Pics_CT %>% arrange(DateTimeOriginal)
    
    



#delta is going to contain the calculated difference of time between species A and B for each row of the detections of the CT
    #but only if the two species from row i and i+1 are in the specific order
    #if the combination of the species names between the row i and i + 1 is equal to the names of the species of interest     stuck togetehr then we calcutalte difftime between the two lines,  otherwise, no
  
    delta <- rep(NA, nrow(Pics_CT_ordered)) # create a empty vector with NAs for calculations later
    
    
    for(i in 1: (nrow(Pics_CT_ordered))) # for each row per B-ordered data set, starting from row 1
      {
      # wenn die Species namenskombi vom foto und dem nächsten Foto gleich ist wie die der gewünschen specieskombi, dann....
      if (paste(Pics_CT_ordered[c(i:(i+1)),"Species"], collapse ="") == paste(species, collapse=""))
        { 
        # Berechne den zeitunterschied zwischen dem Foto und dem nächsten
        diff <- difftime(Pics_CT_ordered[i,"DateTimeOriginal"], Pics_CT_ordered[i+1,"DateTimeOriginal"])
        #if the time difference is more than 12 hours ....
        if (diff < - 12)
          { 
          # then we set it back to zero because it means too much time has spent
          delta[i] <- 0 
        }
        # if not
        if (diff >= -12)
          {
          # we save the time difference in delta
          delta[i] <- diff
          }
        }
      }
    # save delta in the delta species list at the place of k
    delta_species[[numberEle]] <- delta
    # save the name of the CT ID
    names(delta_species)[numberEle] <- as.character(numberCT)
  
    }
  # print(paste0("End Time ", Sys.time()))
  # end.time <- Sys.time()
  # time.taken <- end.time - start.time
  # print(paste0("Time taken ", time.taken))
  return(delta_species)
  
  }
```

# Hier weiter ######
Aber: zunächst sollten in Skript 1 die species names gleich am anfang zu den englischen namen geändert werden. Macht vieles leichter
Dann sollten auch dort diese ganzen Wiederholungen in Funktionen bzw loops gepackt werden. Anstatt dass man alles einzeln auflisten muss

```{r}
# Als function???
#### TEST ####
calc_mean <- function(species_interest) {
  for (i in seq_along(species_interest)) {
    species <- c(species_interest[[i]], species_interest[[i+1]])
    
    delta_species1_species2 <- calculate_delta(species)
    
    df_time_diff_species1_species2 <- plyr::ldply(delta_species1_species2, rbind)
    
    average_diff_species1_species2_id <- df_time_diff_species1_species2 %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_species1_species2[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column
    assign(x = paste("average_diff",species_interest[[i]], species_interest[[i+1]], sep="_"), 
           value = average_diff_species1_species2_id) 
  
  
  }
}


##selecting the species squirrel and cat
species <- c(species_interest[1],species_interest[2])
delta_squirrel_cat <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficient.... sorry
delta_squirrel_cat <- calculate_delta_2(species)
#putting this in a dataframe 
df_time_diff_squirrel_cat1 = plyr::ldply(delta_squirrel_cat, rbind)

##selecting the species raccoon and cat
species = c(species_interest[2],species_interest[1])
delta_raccoon_cat <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_raccoon_cat = plyr::ldply(delta_raccoon_cat, rbind)

##selecting the species cat and fox
species = c(species_interest[1],species_interest[3])
delta_cat_fox <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_cat_fox = plyr::ldply(delta_cat_fox, rbind)

##selecting the species fox and cat
species = c(species_interest[3],species_interest[1])
delta_fox_cat <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_fox_cat = plyr::ldply(delta_fox_cat, rbind)

##selecting the species cat and marten
species = c(species_interest[1],species_interest[4])
delta_cat_marten <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_cat_marten = plyr::ldply(delta_cat_marten, rbind)

##selecting the species marten and cat
species = c(species_interest[4],species_interest[1])
delta_marten_cat <- calculate_delta(species)
#putting this in a dataframe 
df_time_diff_marten_cat = plyr::ldply(delta_marten_cat, rbind)

##selecting the species cat and cat
species = c(species_interest[1],species_interest[1])
delta_cat_cat <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_cat_cat = plyr::ldply(delta_cat_cat, rbind)



##selecting the species fox and raccoon
species = c(species_interest[3],species_interest[2])
delta_fox_raccoon <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_raccoon = plyr::ldply(delta_fox_raccoon, rbind)

##selecting the species raccoon and fox
species = c(species_interest[2],species_interest[3])
delta_raccoon_fox <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_raccoon_fox = plyr::ldply(delta_raccoon_fox, rbind)

##selecting the species fox and marten
species = c(species_interest[3],species_interest[4])
delta_fox_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_marten = plyr::ldply(delta_fox_marten, rbind)

##selecting the species marten and fox
species = c(species_interest[4],species_interest[3])
delta_marten_fox <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_marten_fox = plyr::ldply(delta_marten_fox, rbind)

##selecting the species fox and fox
species = c(species_interest[3],species_interest[3])
delta_fox_fox <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_fox_fox = plyr::ldply(delta_fox_fox, rbind)



#selecting the species raccoon and marten
species = c(species_interest[2],species_interest[4])
delta_raccon_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_raccoon_marten = plyr::ldply(delta_raccon_marten, rbind)

##selecting the species marten and raccoon
species = c(species_interest[4],species_interest[2])
delta_marten_raccoon <- calculate_delta(species) 
#putting this in a dataframe 
df_time_diff_marten_raccoon = plyr::ldply(delta_marten_raccoon, rbind)

##selecting the species raccoon and raccoon
species = c(species_interest[2],species_interest[2])
delta_raccoon_raccoon <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_raccoon_raccoon = plyr::ldply(delta_raccoon_raccoon, rbind)


##selecting the species marten and marten
species = c(species_interest[4],species_interest[4])
delta_marten_marten <- calculate_delta(species) #loop in a loop in a loop I know it's not very efficitent.... sorry
#putting this in a dataframe 
df_time_diff_marten_marten = plyr::ldply(delta_marten_marten, rbind)
```


```{r}
average_diff_squirrel_cat_id1 <- df_time_diff_squirrel_cat1 %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_squirrel_cat1[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_raccoon_id <- df_time_diff_cat_raccoon %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_raccoon[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_cat_id <- df_time_diff_raccoon_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_fox_id <- df_time_diff_cat_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_cat_id <- df_time_diff_fox_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_marten_id <- df_time_diff_cat_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_cat_id <- df_time_diff_marten_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_cat_cat_id <- df_time_diff_cat_cat %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_cat_cat[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column



average_diff_fox_raccoon_id <- df_time_diff_fox_raccoon %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_raccoon[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_fox_id <- df_time_diff_raccoon_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_marten_id <- df_time_diff_fox_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_fox_id <- df_time_diff_marten_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_fox_fox_id <- df_time_diff_fox_fox %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_fox_fox[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column




average_diff_raccoon_marten_id <- df_time_diff_raccoon_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_raccoon_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_marten_raccoon_id <- df_time_diff_marten_raccoon %>%
                              mutate(User_uid = as.numeric(.id)) %>%
                              mutate(mean = rowMeans(df_time_diff_marten_raccoon[,-1], na.rm = T)) %>% #rowmeans
                              dplyr::select(User_uid, mean) #keeping only the mean and the id column

average_diff_raccoon_raccoon_id <- df_time_diff_raccoon_raccoon %>%
                            mutate(User_uid = as.numeric(.id)) %>%
                            mutate(mean = rowMeans(df_time_diff_raccoon_raccoon[,-1], na.rm = T)) %>% #rowmeans
                            dplyr::select(User_uid, mean) #keeping only the mean and the id column



average_diff_marten_marten_id <- df_time_diff_marten_marten %>%
                          mutate(User_uid = as.numeric(.id)) %>%
                          mutate(mean = rowMeans(df_time_diff_marten_marten[,-1], na.rm = T)) %>% #rowmeans
                          dplyr::select(User_uid, mean) #keeping only the mean and the id column

```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
