---
title: "Squirrel activity: Data Preparation" 
description: |
    The aim of the study is to investigate the influence of altered environmental urban parameters and direct human disturbance expressed by the lockdown together with animal predator risk parameters on the general activity of squirrels
author:
    - name: "Sinah Drenske"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-2247-6507
    - name: "Julie Louvrier"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-1252-1746
    - name: "Marius Grabow"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0003-0702-9642
    - name: "Conny Landgraf"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      #orcid_id: 0000-0000-0000-0000
    - name: "Stephanie Kramer-Schadt"
      affiliation: Leibniz Institute for Zoo and Wildlife Research, Technical University Berlin
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0002-9269-4446
    - name: "Aimara Planillo"
      affiliation: Leibniz Institute for Zoo and Wildlife Research
      affiliation_url: https://izw-berlin.de/en/
      orcid_id: 0000-0001-6763-9923
date: "`r Sys.Date()`"
output: 
    distill::distill_article:
        highlight: kate      ## styling of code
        code_folding: true  ## if `true` you can expand and shrink code chunks
        toc: true            ## if `true` adds a table of content
        toc_depth: 4         ## level to be displayed in the table of content
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      dev = "ragg_png", fig.width = 9, fig.height = 6, dpi = 600, retina = 1)
Sys.setlocale("LC_TIME", "C")
```

* **Research question:** Which risk effects increase or decrease the overall activity of red squirrels in urban gardens?  
* **Study area:** Berlin 2019-2020 
* **Data:** Detection histories of squirrels, martens and cats from 4 seasons (spring 2019, autumn 2019, spring 2020, autumn 2020), already filtered as in Louvrier et al. 2021 + environmental information on camera stations. 

# Setup

```{r packages}
#remotes::install_github("EcoDynIZW/d6")
d6::simple_load(c("EcoDynIZW/d6berlin",
                  "here", 
                  "skimr", 
                  "tidyverse"
))
```


# Data

```{r data}
#loading the environmental variables and using only the user IDs that are within the cov table
env_var <- readRDS(here::here("output", 
                              "data-proc", 
                              "01_overall_activity",
                              "ct_focal_covariates_100_20230305.RDS"))
                              #"stacked_raster_values_and_garden_CT_all_seasons_no_nas_proc_20230124.RDS"))

#already formatted and filtered data 
# CT_act_date_proc <- readRDS(here::here("output", "data-proc", "all_seasons",
#                                        "CT_act_date_proc_20230124.RDS"))
CT_species_interest <- readRDS(here::here("output", 
                                          "data-proc", 
                                          "01_overall_activity",
                                          "CT_species_interest_time_20230305.RDS"))
```


Count the number of pictures per species per station 
```{r}
# build a vector for station IDs
station_IDs <- env_var$Station

# Build a table with the number of pictures per species of interest per station
# the full table should have 516 Stations * 3 species = 1548 rows

CT_per_station <- CT_species_interest[, c(1:11)] %>%
  droplevels() %>%
  dplyr::count(Species, Station)  %>% 
  group_by(Species, Station) %>%
  dplyr::summarise(sum_pic = sum(n)) %>%
  ungroup() %>% 
  complete(Station = c(station_IDs), Species, fill = list(sum_pic = 0)) %>%
  full_join(y = env_var[, c(1:20)], by = "Station") %>%
  replace_na(list(Species = "Squirrel", sum_pic = 0)) %>%
  droplevels()

# Squirrels per station
CT_squirrels_station <- CT_per_station %>%
  filter(Species == "Squirrel")

# Calculate a binary column (presence absence) per predator
CT_squirrels_station <- CT_per_station %>%
  filter(Species == "Squirrel") %>% 
  mutate(
    squirrels_cam_binary = case_when(
      Species == "Squirrel" & sum_pic > 0 ~ 1, 
      Species == "Squirrel" & sum_pic == 0 ~ 0)) %>%
  select(Station, squirrels_cam_binary) %>%
  right_join(y = CT_squirrels_station, by = "Station")

CT_squirrels_station <- CT_per_station %>%
  filter(Species == "Cat") %>% 
  mutate(
    cats_cam_binary = case_when(
      Species == "Cat" & sum_pic > 0 ~ 1, 
      Species == "Cat" & sum_pic == 0 ~ 0)) %>%
  select(Station, cats_cam_binary) %>%
  right_join(y = CT_squirrels_station, by = "Station")

CT_squirrels_station <- CT_per_station %>%
  filter(Species == "Marten") %>% 
  mutate(
    marten_cam_binary = case_when(
      Species == "Marten" & sum_pic > 0 ~ 1, 
      Species == "Marten" & sum_pic == 0 ~ 0)) %>%
  select(Station,  marten_cam_binary) %>%
  full_join(y = CT_squirrels_station, by = "Station")
```



Compare cats_binary (cats as pets) and cats_cam_binary
```{r}
table(CT_squirrels_station$cats_binary)
table(CT_squirrels_station$cats_cam_binary) # many more cats on cameras than per garden as pets
table(CT_squirrels_station$marten_cam_binary)
```

Change the column type
```{r}
CT_squirrels_station <- 
  CT_squirrels_station %>%
  dplyr::mutate(across(.cols = c(squirrels_cam_binary, cats_cam_binary, marten_cam_binary), # , raccoon_cam_binary, fox_cam_binary
                       .fns =  as.factor)) %>%
  droplevels()
```

Combine the binary columns with the data per station
```{r}
env_var <- env_var %>%
  left_join(y = CT_squirrels_station[, c(1:4,6)], by = "Station") %>%
  rename(squirrel_pics = sum_pic) %>%
  droplevels()
```

Build a combined table of CT data and environmental data

```{r}
CT_species_interest <- CT_species_interest %>%
  left_join(y = env_var[, c(1, 5:23)], by = "Station") %>%
  droplevels()
```

Build a table only for squirrels
```{r}
CT_squirrels <- CT_species_interest %>%
  filter(Species == "Squirrel") %>%
  droplevels()
```

## Save these data sets
```{r}
# # Environmental data wit squirrel and predator presence
# saveRDS(object = env_var,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "env_var_binary_species_20230305.RDS"))
# 
# # CT species interest with env data
# saveRDS(object = CT_species_interest,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_species_interest_with_env_20230305.RDS"))
# 
# # CT Squirrels
# saveRDS(object = CT_squirrels,
#         file = here::here("output",
#                           "data-proc",
#                           "all_seasons",
#                           "CT_squirrels_20230305.RDS"))
# 
# # CT species of interest per station
# saveRDS(object = CT_per_station,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_species_interest_per_station_20230305.RDS"))
# 
# # CT squirrels per station
# saveRDS(object = CT_squirrels_station,
#         file = here::here("output",
#                           "data-proc",
#                           "01_overall_activity",
#                           "CT_squirrels_per_station_20230305.RDS"))
```


***

<details><summary>Session Info</summary>

```{r sessionInfo}
## DO NOT REMOVE!
## We store the settings of your computer and the current versions of the
## packages used to allow for reproducibility
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
